\chapter{Summary}
\label{ch:summary}

In this thesis, we investigated the application of deep learning for stock price prediction, which is a challenging time series forecasting problem in the financial industry. We studied different markets by selecting correlation features to enhance the accuracy in predicting multiple stock prices, and we developed a novel neural network architecture that combines the Transformer model with Time2Vec technique as Encoder.

As we delved into our investigation, we made a surprising discovery about how well our model works. Through careful testing and analysis, we found that our model performs exceptionally well, better than simpler models and standard ones like LSTM and RNN and better than one-features model. This success is because our model looks at the bigger picture, using a mix of different features that work together seamlessly, setting a new standard for how good predictions can be in our field.

These findings show that using advanced methods for predicting can make a big difference. They also remind us how important it is to think about things like how complicated our model is and which features we use. By paying attention to these details, our study shows us a way to make predictions that work well in real-life situations. This can help people make smarter decisions and gain valuable insights in the financial world and beyond.

In summary, our thesis contributes to the ongoing discourse on the application of deep learning in finance, showcasing the effectiveness of correlation-based features and innovative neural network architectures in improving the accuracy and robustness of stock price prediction models. These advancements hold the promise of facilitating more informed investment decisions and enhancing risk management practices in the ever-evolving landscape of financial markets.
